Malacology: A Programmable Storage System

### 2016-10-05 paper/paper.tex
paper: separate intro and problem
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

To illustrate the benefits and challenges of this approach we examine the
programmability of Ceph~\cite{weil:osdi2006-ceph,ceph}, the increasingly
popular, production-level open-source distributed storage system.  Something of
a storage swiss army knife, Ceph supports file, block, and object interfaces
simultaneously in a single cluster~\cite{ceph_contributors_ceph_2010}. Ceph's
Reliable Autonomous Distributed Object Storage (RADOS) system is a cluster of
storage devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

To illustrate the benefits and challenges of this approach we have designed and
evaluated Malacology, a programmable storage system for constructing new
services by re-purposing existing subsystem abstractions contained in Ceph. We
build the framework in Ceph by leveraging a broad spectrum of existing
services, including distributed locking and caching services provided by MDSs,
durability and logical storage devices provided by RADOS, and propagation of
consistent cluster state provided by the monitoring service (see
Figure~\ref{fig:overview}). As we will show in this paper, this framework is
expressive enough to provide the functionality necessary for implementing new
services. Our contributions are:

@@

\begin{enumerate}
%  \def\labelenumi{\arabic{enumi}.}
%  \itemsep1pt\parskip0pt\parsep0pt

@@

\begin{enumerate}
%  \def\labelenumi{\arabic{enumi}.} \itemsep1pt\parskip0pt\parsep0pt
\item A high-performance distributed shared log service called ZLog which is
based on CORFU~\cite{balakrishnan_corfu_2012}

@@

>>>>

To illustrate the benefits and challenges of this approach we have designed and
evaluated Malacology, a programmable storage system for constructing new
services by re-purposing existing subsystem abstractions of the storage stack.
We build the framework in Ceph by leveraging a broad spectrum of existing
services, including distributed locking and caching services provided by
metadata servers, durability and logical storage devices provided by the
backend object store, and propagation of consistent cluster state provided by
the monitoring service (see Figure~\ref{fig:overview}). As we will show in this
paper, this framework is expressive enough to provide the functionality
necessary for implementing new services. Our contributions are:

@@

\begin{enumerate}

@@

\begin{enumerate}

\item A high-performance distributed shared log service called ZLog which is
based on CORFU~\cite{balakrishnan_corfu_2012}

@@

\section{Highly Tailored, Application-Specific Storage Stacks
}\label{highly-tailored-and-application-specifc-storage-systems}

To illustrate the benefits and challenges of this approach we examine the

Today's storage stacks are large, monolothic systems built to ensure
scalability and persistence -- a storage system that loses user's data is
useless. Building storage stacks from the ground up for a specific purpose
results in the best performance. For example, HDFS was designed specifically to
server Hadoop's jobs and relaxes POSIX constraints~\cite{CITEME}.
Alternatively, general-purpose storage stacks are built with the flexiblity to
serve many applications by embedding tunable parameters to control low level
implementation details like block size. Unfortunately, users want more control
from the general-purpose storage stacks without going as far as building their
storage system from the ground up.

% does this belong?
To demonstarte the need for programmability in storage systems, we examine
Ceph's programmability. Ceph~\cite{weil:osdi2006-ceph,ceph}, the increasingly
popular, production-level open-source distributed storage system, was
originally built to be an HPC file system. But demands for storage systems that
could slide in behind cloud infrastructures, like OpenStack, shifted the focus
to Ceph's internal object store as a back end for large cloud block devices,
S3-like objects, and file system workloads.  Something of a storage swiss army
knife, Ceph supports file, block, and object interfaces simultaneously in a
single cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous
Distributed Object Storage (RADOS) system is a cluster of storage devices
(OSDs) that provide Ceph with data durability and integrity using replication,
erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing programmability concepts into Ceph, we can build new services
% by carefully exposing internal storage services to applications.
